Bandit Multiclass Classification

### 2018-10-11 ptf_margin.tex
started rational approximation

\subsection{Construction using rational functions}

>>>>

\subsection{Construction using rational functions}
\paragraph{The construction.} Define
\[
  Q(x) = \sum_{i=1}^t S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t - \frac 1 2).
\]
where function
\[
S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}} = \frac{A_n^k(x)}{B_n^k(x)},
\]
$h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.

\begin{lemma}[~\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
\end{lemma}
\begin{proof}
We consider two cases regarding the label of the example.
\end{proof}

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n(x)$ is in $[1, 1 + \frac 1 k]$.
\item If $x$ is in $[2^{-n}, -1]$, then $S_n(x)$ is in $[-1 - \frac 1 k, -1]$.
\item If $x$ is in $[-1, 1]$, then $|S_n(x)|$ is in $[-1, 1]$.
\item For all $x$ in $\fR$, $|B_n^k(x)| \geq \frac{2k}{2k+1} 2^{\frac{n(n-1)h(k)}2}$.
\end{enumerate}
\end{fact}
